### 2014-09-23 paper/include/techniques.tex
wrote about A
worked on A

\section{Intelligent Refresh Techniques} 
\label{sec:int}

\subsection{Access Recency}
DRAM accesses imply refresh operations, and so a subsequent refresh to the same row can be postponed. The number of rows affected depends on how many different rows are accessed within the maximum refresh period, which may be few for many workloads. Ghosh et al. [9] propose Smart Refresh, which divides the refresh period into phases and maintains a per-row timeout counter in the MC. The MC decrements the counters each phase and issues a RAS-only refresh when a counter hits zero.

>>>>

\section{Methods for decreasing the refresh rate} 
\label{sec:met}
There are several methods that can be applied to decrease the refresh rate and these can be categorized depending on with sort of information the scheduling decisions are based upon. The four sort of information are: access recency, cell retention times, error tolerance of the data, and line validity. This categorization follows the taxonamy proposed by authors \cite{dtail}. 
\subsection{Access Recency}
DRAM accesses imply refresh operations, and so a subsequent refresh to the same row can be postponed. The number of rows affected depends on how many different rows are accessed within the maximum refresh period, which may be few for many workloads. Ghosh et al. [9] propose Smart Refresh, which divides the refresh period into phases and maintains a per-row timeout counter in the MC. The MC decrements the counters each phase and issues a RAS-only refresh when a counter hits zero.
